Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-15 papers/thesis-kirstie/thesis.tex
more edits

Classically, fluids have been modeled by a collection of small, impenetrable spheres colliding 
with one another like billiard balls%~\cite{kinetictheory}
. This model, called the Hard-Sphere fluid, has served as 
the primary reference system for fluids. This is due to the fact that the repulsion between atoms is 
much stronger than their attraction, and so the repulsive potential, which is descriptive of hard spheres, 
dominates the interactions between atoms.

@@

\begin{figure}[h!]
    \centering
      % FIXME \includegraphics[height=3.5cm]{TwoSpheres.pdf} 
    \caption{(Left) The WCA potential is a minimum at r=2R. 
             (Right) The WCA potential increases rapidly for $r<2R$.}
    \label{fig:TwoSpheres}
    \end{figure}

@@

\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\[{}\]
\begin{figure}
 \centering
  %\includegraphics[width=\columnwidth]{figs/Phase_Diagram_of_T_vs_n}
\caption{Phase Diagram of the reduced termperature verses the reduced density. Green lines indicate the region of coexistence from Monte-Carlo simulations.}
\label{fig:Phase_Diagram_of_T_vs_n}
\end{figure}

\begin{figure}
 \begin{center}
  %\includegraphics[width=\columnwidth]{figs/Phase_Diagram_of_P_vs_T}
 \end{center}
\caption{Phase Diagram of the reduced pressure verses the reduced temperature. The green line marks the boundary from Monte-Carlo simulations.}
\label{fig:Phase_Diagram_P_vs_T}
\end{figure}

>>>>

Classically, fluids have been modeled by a collection of small, impenetrable spheres colliding 
with one another like billiard balls. In the simplest case, the spheres are treated as having 
only a replulsive potential. This model, called the Hard-Sphere fluid, has served as the primary 
reference system for fluids. This is due to the fact that the repulsion between atoms is much 
stronger than their attraction, and so the repulsive potential, which is descriptive of 
hard spheres, dominates the interactions between atoms.

@@

\begin{figure}[h!]
    \centering
    %\includegraphics[height=3.5cm]{TwoSpheres.pdf} 
    \caption{(Left) The WCA potential is a minimum at r=2R. 
             (Right) The WCA potential increases rapidly for $r<2R$.}
    \label{fig:TwoSpheres}
    \end{figure}

@@

\begin{figure}
 \centering
 %\includegraphics[width=\columnwidth]{figs/Phase_Diagram_of_T_vs_n}
\caption{Phase Diagram of the reduced termperature verses the reduced density. Green lines indicate the region of coexistence from Monte-Carlo simulations.}
\label{fig:Phase_Diagram_of_T_vs_n}
\end{figure}

\begin{figure}
 \centering
 %\includegraphics[width=\columnwidth]{figs/Phase_Diagram_of_P_vs_T}
\caption{Phase Diagram of the reduced pressure verses the reduced temperature. The green line marks the boundary from Monte-Carlo simulations.}
\label{fig:Phase_Diagram_P_vs_T}
\end{figure}
